Flip score characterisation

### 2018-08-10 manuscript/supplementary_notes/metric_conformity/metric_conformity.Rmd

---
title: "Metric conformity"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
mainfont: DejaVu Sans
---

@@

```{r}
assessments %>%
  left_join(rules %>% select(id, name), by = c("rule_id" = "id")) %>%
  unnest(conformity) %>%
  mutate(
    metric_id = label_metrics(metric_id, label_type = "latex") %>% paste0("$", ., "$") %>% forcats::fct_inorder(),
    conforms = kableExtra::cell_spec(
      ifelse(conforms, "\U2714", "\U2716"),
      background = ifelse(conforms, "#2ECC40", "#FF4136"),
      format = "latex"
    )
  ) %>%
  spread(metric_id, conforms) %>%
  select(-rule_id) %>% 
  knitr::kable(format = "latex", escape = FALSE) %>%
  kableExtra::kable_styling(row_label_position = "r")
```

@@

walkdf(assessments[1, ], function(assessment) {
  cat(knitr::knit_child("assessment.Rmd", quiet=TRUE, envir = environment()))
})
```

>>>>

---
title: "Metric conformity"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: true
header-includes:
  - \usepackage{tabularx}
mainfont: DejaVu Sans
---

@@

```{r}
assessments %>%
  left_join(rules %>% select(id, name), by = c("rule_id" = "id")) %>%
  unnest(conformity) %>%
  mutate(
    metric_id = label_metrics(metric_id, label_type = "latex") %>% paste0("$", ., "$") %>% forcats::fct_inorder(),
    conforms = kableExtra::cell_spec(
      ifelse(conforms, "\U2714", "\U2716"),
      background = ifelse(conforms, "#2ECC40", "#FF4136"),
      format = "latex"
    ),
    rule_id = forcats::fct_inorder(rule_id)
  ) %>%
  spread(metric_id, conforms) %>%
  select(-rule_id) %>% 
  knitr::kable(format = "latex", escape = FALSE, booktabs = TRUE) %>%
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::column_spec(1, width="15em") %>% 
  kableExtra::column_spec(2:20, width = "3em") %>% 
  kableExtra::row_spec(0, angle = 30) %>% 
  gsub("\\\\addlinespace", "", .)
```

@@

walkdf(assessments[, ], function(assessment) {
  cat(knitr::knit_child("assessment.Rmd", quiet=TRUE, envir = environment()))
})
```

### 2018-08-10 scripts/01-datasets/02-synthetic/README.Rmd

These are estimated in [01-estimate_platform.R](01-estimate_platform.R).

@@

>>>>

These are estimated in [01-estimate_platform.R](01-estimate_platform.R) and are called "platforms".

@@

Each simulation script (02a-02d) first creates a design dataframe, which links particular platforms, different topologies, seeds and other parameters specific for a simulator.

Next it calls the wrappers around the simulators (see [/package/R/simulators.R](/package/R/simulators.R))

### 2018-08-10 scripts/03-metric_characterisation/02-metric_examples/4-edge_flip.Rmd

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynbenchmark)
library(tidyverse)
library(dyneval)
library(cowplot)
```

```{r}
experiment("3-score_rules/4-edge_flip")

knitr::opts_chunk$set(echo = TRUE)
```

Generate different trajectory topologies
```{r}
topologies <- eval(formals(dyntoy:::generate_milestone_network)$model)
topologies <- topologies[topologies != "BA"]
networks_synthetic <- map(topologies, dyntoy:::generate_milestone_network) %>% tibble(milestone_network = ., topology = topologies)
```

Add SCORPIUS predictions
```{r}
ti_methods <- list(ti_scorpius())
data <- dyntoy::generate_toy_datasets(c("linear"), num_replicates=1, num_cells=30, num_genes=10) %>% dynutils::extract_row_to_list(1)

results <- map(ti_methods, ~.$run_fun(data$counts))

networks_methods <- tibble(topology=map_chr(ti_methods, "name"), milestone_network=map(results, "milestone_network"))
```

```{r}
networks <- bind_rows(networks_synthetic, networks_methods)
design <- crossing(networks, networks)
```

@@

  start <- Sys.time()
  score <- dyneval:::calculate_edge_flip(milestone_network, milestone_network1)
  time <- Sys.time() - start
  tibble(score=score, time=time)
}) %>% bind_rows()
design <- bind_cols(design, scores)

>>>>

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
library(dynbenchmark)
library(tidyverse)
library(dyneval)
library(cowplot)

experiment("03-score_rules/02-metric_examples")
```

Generate different trajectory topologies
```{r}
topologies <- eval(formals(dyntoy:::generate_milestone_network)$model)
networks <- map(topologies, dyntoy:::generate_milestone_network) %>% tibble(milestone_network = ., topology = topologies)

design <- crossing(networks, networks)
```

@@

  start <- Sys.time()
  score <- dyneval:::calculate_edge_flip(milestone_network, milestone_network1, limit_flips = 10)
  time <- Sys.time() - start
  tibble(score=score, time=time)
}) %>% bind_rows()
design <- bind_cols(design, scores)
